Kit Theory

### 2023-06-21 paper/paper.tex
Update.

  \section{Substitution \& Renamings}
  Our sort-indexed syntax allows us to define substitutions and
  renamings which replace variables of all sorts simultaneously:

@@

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  Similarly a substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms from \texttt{S₂}.
  We consider these operations \emph{very parallel}, because they do not just replace all variables of one sort in parallel, but they replace all variables of all sorts in parallel.

>>>>

  \section{Substitution \& Renamings}
  Our sort-indexed syntax allows us to define substitutions and
  renamings which replace all variables of all sorts simultaneously:

@@

  A renaming \texttt{S₁ →ᵣ S₂} maps variables from \texttt{S₁} to
  variables from \texttt{S₂}.
  A substitution \texttt{S₁ →ₛ S₂} maps variables from \texttt{S₁} to
  terms from \texttt{S₂}.
